*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-09 Code/Manuscript_O2.Rmd
Knitted new GAM figures

knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MED4_Oxy_.png"))

@@

knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_SS120_Oxy_.png"))

@@

knitr::include_graphics(file.path(FiguresIn, "PICO_Hypervolume_GAM_MIT9313_Oxy_.png"))

>>>>

knitr::include_graphics(file.path(FiguresIn, "MED4GAM.png"))

@@

knitr::include_graphics(file.path(FiguresIn, "SS120GAM.png"))

@@

knitr::include_graphics(file.path(FiguresIn, "MIT9313GAM.png"))
